---
title: "agenor_v2"
author: "Matthew J. Murphy"
date: "`r Sys.Date()`"
output: html_document
---

# Preprocessing steps

## Set working directory

```{r, warning=F, message=F}
setwd("C:/Users/mmurph36/OneDrive - Brown University/Documents/nsfg")

#install.packages("haven")
install.packages("survey", repos = "http://cran.us.r-project.org")
#install.packages("tidyverse")
#install.packages("margrittr")
#install.packages("plyr")
#install.packages("gtsummary")

#library(haven)
library(survey)
#library(tidyverse)
#library(magrittr)
#library(plyr)
#library(gtsummary)
```

## Read in 2011-2019 fem resp and preg .rds files

```{r}
preg1 <- readRDS("2011_2013_FemPregData.rds")
fem1 <- readRDS("2011_2013_FemRespData.rds")
preg2 <- readRDS("2013_2015_FemPregData.rds")
fem2 <- readRDS("2013_2015_FemRespData.rds")
preg3 <- readRDS("2015_2017_FemPregData.rds")
fem3 <- readRDS("2015_2017_FemRespData.rds")
preg4 <- readRDS("2017_2019_FemPregData.rds")
fem4 <- readRDS("2017_2019_FemRespData.rds")
```

## Create one large preg and fem files for 2011-2019

```{r}
preg <- data.table::rbindlist(list(preg1, preg2, preg3, preg4), fill = T)
fem <- data.table::rbindlist(list(fem1, fem2, fem3, fem4), fill = T)

nrow(preg) # 38669 pregnancy records
nrow(fem) # 22995 female respondent records
```

## Scrape sexual orientation variable from 'fem' data.table

`orient_a` was "USED IN RANDOM HALF SAMPLE OF NSFG RESPONDENTS"
 
- 1 = Heterosexual or straight
- 2 = Homosexual, gay, or lesbian
- 3 = Bisexual

`orient_b` was "USED IN RANDOM HALF SAMPLE OF NSFG RESPONDENTS"
 
- 1 = Lesbian or gay
- 2 = Straight, that is not lesbian or gay
- 3 = Bisexual
- 4 = Something else

```{r, message=F, warning=F}
library(tidyverse)

orients <- fem %>% select(caseid, orient_a, orient_b)

orients$myorient <- rep(NA, nrow(orients))
orients$myorient[orients$orient_a == 1 | orients$orient_b == 2] <- "Heterosexual"
orients$myorient[orients$orient_a == 2 | orients$orient_b == 1] <- "Lesbian"
orients$myorient[orients$orient_a == 3 | orients$orient_b == 3] <- "Bisexual"

length(which(orients$myorient %in% c("Heterosexual", "Lesbian", "Bisexual"))) 
# N = 11,283 myorient values of interest

# given a list of 11,283 orients and their caseid's, we want to merge so that all caseid's 
# occurring in both data frames have their orientation added in the orients column
nsfg_data <- merge(x = preg,
                   y = orients, 
                   by = "caseid")

nsfg_data <- nsfg_data %>% subset(!is.na(myorient))
nrow(nsfg_data) #mapped onto 19,029 pregnancies
```

## Merge weights data.frame into nsfg_data by 'caseid'

```{r}
weightsFrame <- readRDS("2011_2019_FemaleWgtData.rds")

# join
nsfg_data <- merge(x = nsfg_data, 
             y = weightsFrame, 
             by="caseid")

```

## Subset nsfg_data by age (between 15 and 45)

```{r}
# Create your age subset... 
length(nsfg_data$caseid) # 19,029 pregnancies of interest

length(which(nsfg_data$agepreg < 15 | 
             nsfg_data$agepreg > 45 | 
             is.na(nsfg_data$agepreg))) # 550 fall outside of age range

nsfg_data <- nsfg_data %>% subset(agepreg >= 15 & agepreg <= 45)

length(nsfg_data$caseid) # leaves us w/ 18,479 pregnancies of interest
```

## Create 'myrace'

```{r}
# create myrace
nsfg_data$myrace <- rep(NA, nrow(nsfg_data))
nsfg_data$myrace[nsfg_data$hisprace2 == 1] <- "Latina"
nsfg_data$myrace[nsfg_data$hisprace2 == 2] <- "White"
nsfg_data$myrace[nsfg_data$hisprace2 == 3] <- "Black"
```

```{r}
nsfg_data <- nsfg_data %>% subset(!is.na(myrace))
nrow(nsfg_data)
```

## Create eventual strata

-   1 = White Heterosexual
-   2 = Black Heterosexual
-   3 = Latina Heterosexual
-   4 = White Bisexual
-   5 = Black Bisexual
-   6 = Latina Bisexual
-   7 = White Lesbian
-   8 = Black Lesbian
-   9 = Latina Lesbian

```{r}

nsfg_data$mystrata <- rep(NA, nrow(nsfg_data))

nsfg_data$mystrata[nsfg_data$myrace == "White" & 
                     nsfg_data$myorient == "Heterosexual"] <- 1

nsfg_data$mystrata[nsfg_data$myrace == "Black" & 
                     nsfg_data$myorient == "Heterosexual"] <- 2

nsfg_data$mystrata[nsfg_data$myrace == "Latina" & 
                     nsfg_data$myorient == "Heterosexual"] <- 3

###############################################################################

nsfg_data$mystrata[nsfg_data$myrace == "White" & 
                     nsfg_data$myorient %in% c("Lesbian", "Bisexual")] <- 4

nsfg_data$mystrata[nsfg_data$myrace == "Black" & 
                     nsfg_data$myorient  %in% c("Lesbian", "Bisexual")] <- 5

nsfg_data$mystrata[nsfg_data$myrace == "Latina" & 
                     nsfg_data$myorient  %in% c("Lesbian", "Bisexual")] <- 6

```

```{r}
nsfg_data <- nsfg_data %>% subset(!is.na(wgt2011_2019))
nrow(nsfg_data) 

# N = 13,742 pregnancies with non-NA weights
```

###############################################################################

# Get testing vars from 'fem' files
```{r}
testing <- fem %>% select(caseid, pap12, stdsvc12)

# join
nsfg_data <- merge(x = nsfg_data, 
             y = testing, 
             by="caseid")

nrow(nsfg_data)
```

###############################################################################

# Get N (%) for `mystrata`

```{r}
table(nsfg_data$mystrata, exclude = NULL)
prop.table(table(nsfg_data$mystrata))*100
```

###############################################################################

# Create categorical variables for Table 1

## Create `tbl1_age` var for age

1 = 15-19
2 = 20-29
3 = 30+

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_age = ifelse(agepreg >= 15 & agepreg <= 19, 1,
                           ifelse(agepreg >= 20 & agepreg <= 29, 2, 3)))
```

## Create `tbl_usBorn` var for us born

1 = us born
2 = not us born
NA = NA

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_usBorn = ifelse(brnout == 5, 1,
                           ifelse(brnout == 1, 2, NA)))
```

## Create `tbl1_residence` var for place of residence

1 = city of msa
2 = other msa
3 = not msa
NA = NA

```{r}
nsfg_data$tbl1_residence <- nsfg_data$metro
```

## Create `tbl1_relationship` var for relatioship status

1 = never married
2 = currently married to a male partner
3 = not married but living with a male partner
4 = separated, divorced, or widowed

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_relationship = ifelse(rmarital == 6, 
                                    1,
                                    ifelse(rmarital == 1, 
                                           2,
                                           ifelse(rmarital == 2, 
                                                  3,
                                                  ifelse(rmarital %in% c(3,4,5), 
                                                         4,NA)))))
```

## Create `tbl1_education` var for educational attainment

1 = less than high school
2 = high school diploma
3 = some college, associate's degree
4 = bachelor's degree or higher

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_education = ifelse(hieduc %in% c(5,6,7,8), 
                                 1,
                                    ifelse(hieduc == 9, 
                                           2,
                                           ifelse(hieduc %in% c(10,11), 
                                                  3,
                                                  ifelse(hieduc %in% c(12,13,14,15), 
                                                         4, NA)))))
```


## Create `tbl_householdFPL` var for household federal poverty level (%)

1 <100
2 100-199
3 200-299
4 >=300

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_householdFPL = ifelse(poverty %in% c(0:99),
                                    1,
                                    ifelse(poverty %in% c(100:199), 
                                           2,
                                           ifelse(poverty %in% c(200:299), 
                                                  3,
                                                  ifelse(poverty %in% c(300:700), 
                                                         4, NA)))))
```


## Create `tbl1_employment` var for employment status

1 = working for pay
2 = not working for pay
3 = student

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_employment = ifelse(laborfor %in% c(1,2,3,4), 1,
                                  ifelse(laborfor %in% c(5,7,8,9), 2,
                                         ifelse(laborfor == 6, 3, NA))))

```


## Create `tbl1_healthInsurance` var for health insurance status

1 = private
2 = public
3 = under-insured or uninsured
NA = NA

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_healthInsurance = ifelse(curr_ins == 1, 1,
                                       ifelse(curr_ins %in% c(2,3), 2,
                                              ifelse(curr_ins == 4, 3, NA))))
```


## Create `tbl_pap12` var for yes to pap test in past 12 months

1 = yes
2 = no
NA = NA

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_pap12 = ifelse(pap12 == 1, 1,
                             ifelse(pap12 == 5, 2, NA)))
```


## Create `tbl1_sti12` var for yes to STI test in past 12 months

1 = yes
2 = no
NA = NA

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(tbl1_sti12 = ifelse(stdsvc12 == 1, 1,
                             ifelse(stdsvc12 == 5, 2, NA)))
```

## Create `prenat_care` var for Y/N

```{r}
nsfg_data <- nsfg_data %>% 
  mutate(prenat_care = ifelse(pncarewk %in% c(1,2), 1,
                              ifelse(pncarewk == 3, 0, NA)))
```

## Make `mystrata_factor`
```{r}
nsfg_data$mystrata_factor <- as.factor(nsfg_data$mystrata)
```

```{r}
nsfg_data$id_12 <- ifelse(nsfg_data$mystrata_factor == 1, 0,
                          ifelse(nsfg_data$mystrata_factor == 2, 1, NA))

nsfg_data$id_13 <- ifelse(nsfg_data$mystrata_factor == 1, 0,
                          ifelse(nsfg_data$mystrata_factor == 3, 1, NA))

nsfg_data$id_14 <- ifelse(nsfg_data$mystrata_factor == 1, 0,
                          ifelse(nsfg_data$mystrata_factor == 4, 1, NA))

nsfg_data$id_15 <- ifelse(nsfg_data$mystrata_factor == 1, 0,
                          ifelse(nsfg_data$mystrata_factor == 5, 1, NA))

nsfg_data$id_16 <- ifelse(nsfg_data$mystrata_factor == 1, 0,
                          ifelse(nsfg_data$mystrata_factor == 6, 1, NA))
```

###############################################################################

# Set nsfg_design

```{r}
nsfg_design <- svydesign(id = ~1, 
                         weights = ~nsfg_data$wgt2011_2019, 
                         data = nsfg_data)
```

# Get proportions for Table 1

## `tbl1_age` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_age), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_age + mystrata_factor), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_usBorn` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_usBorn), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_usBorn + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_residence` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_residence), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_residence + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_relationship` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_relationship), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_relationship + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_education` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_education), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_education + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_householdFPL` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_householdFPL), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_householdFPL + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_employment` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_employment), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_employment + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_healthInsurance` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_healthInsurance), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_healthInsurance + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_pap12` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_pap12), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_pap12 + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

## `tbl1_sti12` by `mystrata`

```{r}
round(prop.table(svytable((~tbl1_sti12), nsfg_design))*100, digits = 3)

round(prop.table(svytable((~tbl1_sti12 + mystrata), 
                          nsfg_design), margin = 2)*100, digits = 3)
```

###############################################################################

```{r}
nsfg_design <- svydesign(id = ~1, 
                         weights = ~nsfg_data$wgt2011_2019, 
                         data = nsfg_data)
```

```{r}
svyby(formula = ~prenat_care, 
            by = ~mystrata_factor, 
            design = nsfg_design, 
            FUN = svyciprop, 
            vartype = "ci")
```


```{r}
svychisq(formula = ~prenat_care+id_16,
         design = nsfg_design, 
         statistic = "adjWald")
```

```{r}
logit1 <- (svyglm(prenat_care~mystrata_factor, 
                  family=quasibinomial, 
                  design=nsfg_design, 
                  na.action = na.omit))
summary(logit1)
exp(coef(logit1))
exp(confint(logit1))
```

```{r}
logit2 <- (svyglm(prenat_care~mystrata_factor +
                    relevel(as.factor(tbl1_age), ref = 2) +
                    relevel(as.factor(tbl1_residence), ref = 1) +
                    relevel(as.factor(tbl1_usBorn), ref = 1) +
                    relevel(as.factor(tbl1_relationship), ref = 1),
                  family=quasibinomial, 
                  design=nsfg_design, 
                  na.action = na.omit))
summary(logit2)
exp(coef(logit2))
exp(confint(logit2))
```


```{r}
logit3 <- (svyglm(prenat_care~mystrata_factor +
                    relevel(as.factor(tbl1_age), ref = 2) +
                    relevel(as.factor(tbl1_residence), ref = 1) +
                    relevel(as.factor(tbl1_usBorn), ref = 1) +
                    relevel(as.factor(tbl1_education), ref = 4) +
                    relevel(as.factor(tbl1_householdFPL), ref = 4) +
                    relevel(as.factor(tbl1_employment), ref = 1),
                  family=quasibinomial, 
                  design=nsfg_design, 
                  na.action = na.omit))
summary(logit3)
exp(coef(logit3))
exp(confint(logit3))
```

```{r}
logit4 <- (svyglm(prenat_care~mystrata_factor +
                    relevel(as.factor(tbl1_age), ref = 2) +
                    relevel(as.factor(tbl1_residence), ref = 1) +
                    relevel(as.factor(tbl1_usBorn), ref = 1) +
                    relevel(as.factor(tbl1_education), ref = 4) +
                    relevel(as.factor(tbl1_householdFPL), ref = 4) +
                    relevel(as.factor(tbl1_employment), ref = 1) +
                    relevel(as.factor(tbl1_healthInsurance), ref = 1) +
                    relevel(as.factor(tbl1_pap12), ref = 1) +
                    relevel(as.factor(tbl1_sti12), ref = 1),
                  family=quasibinomial, 
                  design=nsfg_design, 
                  na.action = na.omit))
summary(logit4)
exp(coef(logit4))
exp(confint(logit4))
```

###############################################################################

```{r}
newdata <- as_tibble(predict(logit2, nsfg_data, type="response", se=TRUE))

#plot_df <- bind_cols(nsfg_data, newdata)

#ggplot(data=plot_df, aes(x=mystrata_factor, y=fit)) +
#  geom_boxplot() +
#  xlab("")
```
